### 2020-03-22 thesis_template/3_Body/model/merge_sort_experiment.tex
redo experiment for mergesort

This experiment is to assess importance of careful memory management in multithreading of Rust. 
We implement merge-sort algorithm in two different ways. One is sharing source vector with Arc. 
The other is passing slice of source vector to child thread.

@@

@@

>>>>

\subsection{Description}
This experiment is to assess importance of careful memory management in multithreading of Rust. 
In Rust programming, we usually need Atomic Reference Counting (Arc) to share data among threads. 
However, 
We implement merge-sort algorithm in two different ways. One is sharing source vector with Arc. 
The other is passing slice of source vector to child thread.

@@

\subsection{Result}

@@

\subsection{Discussion}

### 2020-03-22 thesis_template/3_Body/model/tree_aggregate_experiment.tex
document chabged
redo experiment for mergesort

The other way is to get reference to the elements. Since an original source vector is deallocated after a local aggregation,
Simple reference to elements does not live long enough and allow the aggregation result to be sent to next node. 
Instead of simple borrowing, we need owner in the aggregation result. Reference Counting (Rc) in Rust is a way to have multiple owners to a value. 
Since our experiment is implemented in multithreading, Atomic Reference Counting (Arc) is used instead of Rc. With Arc, multiple ownership pointer can be 
possessed by different variables across multiple threads. Therefore a value is not deallocated until all of owners to it are dropped. 
This does not require extra memory allocation, because only acquisition of new ownership to value is needed. 
However, deletion of Arc type checks whether the value is still owned by other variables. 
This checking may be a overhead in algorithms where generate a lot of intermediate data structures, because deletion of the data structures occurs in frequent.

Two algorithms are implemented using the above two different methods and evaluated their runtime performance. 
The both algorithms perform tree-aggregation where runs seven nodes. 
Each node load Customer vector from disk and aggregate it by Customer last name. Once a node finishes aggregation, it sends result to parent node. 
After parent nodes receive aggregation results from all of its children nodes, it joins all aggregation results including its and sends next parent. 
One algorithm performs aggregation by deep-copying elements from source vector loaded from disk. In the other algorithm, each element of source vector 
is wrapped in Arc, and its reference is acquired while aggregation.

@@

The result shows a deep-copy of Customer vector is computationally much more expensive than acquisition and deletion of Arc. 
This result suggests that having element objects in Arc is efficient than deep-copying element from original source vector in tree-aggregation algorithm 
where generates intermediate data structure. The intermediate data structure can be seen in traditional Big Data tool.

>>>>

The other way is to get reference to the elements. Since an original source vector is deallocated after a local aggregation,
Simple reference to elements does not live long enough and allow the aggregation result to be sent to next node. 
Instead of simple borrowing, we need owner in the aggregation result. Reference Counting (Rc) in Rust is a way to have multiple owners to a value. 
Since our experiment is implemented in multithreading, Atomic Reference Counting (Arc) is used instead of Rc. With Arc, multiple ownership pointer can be 
possessed by different variables across multiple threads. Therefore a value is not deallocated until all of owners to it are dropped. 
This does not require extra memory allocation, because only acquisition of new ownership to value is needed. 
However, deletion of Arc type checks whether the value is still owned by other variables. 
This checking may be an overhead in algorithms where generate a lot of intermediate data structures, because deletion of the data structures occurs in frequent.

Two algorithms are implemented using the above two different methods and evaluated their runtime performance. 
The both algorithms perform tree-aggregation where runs on seven partitions of source vector. 
Each steps load Customer vector from disk and aggregate it by Customer last name. Once a node finishes aggregation, it sends result to parent node. 
After parent nodes receive aggregation results from all of its children nodes, it joins all aggregation results including its and sends next parent. 
One algorithm performs aggregation by deep-copying elements from source vector loaded from disk. In the other algorithm, each element of source vector 
is wrapped in Arc, and its reference is acquired while aggregation.

@@

The result shows a deep-copy of Customer vector is computationally much more expensive than acquisition and deletion of Arc. 
This result suggests that having element objects in Arc is efficient than deep-copying element from original source vector in tree-aggregation algorithm 
where generates intermediate data structure.

\begin{figure}[htb]
    \begin{lstlisting}
        fn aggregate_local(arr :&[Arc<CustomerOwned>]) 
        {   
            let mut agg = HashMap::new();
            let n = arr.len();
            for i in 0..n {
                let customer = Arc::clone(&arr[i]);
                let last_name = customer.last_name.clone();
                let vector = agg.entry(last_name).or_insert_with(Vec::new);
                vector.push(customer);
            }
            return agg;
        }
    \end{lstlisting}
    \caption{Aggregation function with Arc}
    \label{fig:Sampling}
\end{figure}

\begin{figure}[htb]
    \begin{lstlisting}
        fn aggregate_local_copy(arr :&[CustomerOwned]) 
        {   
            let mut agg = HashMap::new();
            let n = arr.len();
            for i in 0..n {
                let customer = arr[i].clone();
                let last_name = customer.last_name.clone();
                let vector = agg.entry(last_name).or_insert_with(Vec::new);
                vector.push(customer);
            }
            return agg;
        }
    \end{lstlisting}
    \caption{Aggregation function with deep-copy}
    \label{fig:Sampling}
\end{figure}
